Data Analysis Expanded

### 2019-08-20 data_analysis/data_analysis_expanded.Rmd
routine update

```{r s1_m4_b}
set.seed(24)
s1_m4_b <- rre::cv_replicates(list_of_samples[[2]],
                              eval_function = "gof_chi_sq",
                              partitions = 5,
                              lambda_vec = seq(0,300,by=20),
                              multiplier = 200,
                              c_seq_len = 50,
                              starts = big_starts)
```
```{r s1_m4_b_print, results = 'asis'}
s1_m4_b %>% report_results_2(., list_of_samples[[1]])
```

@@

```{r s2_m4_b}
set.seed(2345)
s2_m4_b <- rre::cv_replicates(list_of_samples[[2]],
                              eval_function = "gof_chi_sq",
                              partitions = 5,
                              lambda_vec = seq(0,200,by=20),
                              multiplier = 200,
                              c_seq_len = 50,
                              starts = big_starts)
```
```{r s2_m4_b_print, results = 'asis'}
s2_m4_b%>% report_results_2(., list_of_samples[[2]])
```

@@

```{r s3_m4_a}
# big grids and few partitions to start:
set.seed(7654)
s3_m4_a <- rre::cv_replicates(list_of_samples[[3]],
                              eval_function = "gof_chi_sq",
                              partitions = 5,
                              lambda_vec = seq(0,1000,by=200),
                              multiplier = 200,
                              c_seq_len = 20)
```
```{r s3_m4_a_print, results = 'asis'}
s3_m4_a %>% report_results_2(., list_of_samples[[3]])
```

@@

```{r s3_m4_b}
# big grids and few partitions to start:
set.seed(7654)
s3_m4_b <- rre::cv_replicates(list_of_samples[[3]],
                              eval_function = "gof_chi_sq",
                              partitions = 5,
                              lambda_vec = seq(0,200,by=20),
                              multiplier = 200,
                              c_seq_len = 50,
                              starts = big_starts)
```
```{r s3_m4_b_print, results = 'asis'}
s3_m4_b %>% report_results_2(., list_of_samples[[3]])
```

>>>>

```{r s1_m4_b}
set.seed(24)
s1_m4_b <- rre::cv_replicates(list_of_samples[[2]],
                              eval_function = "gof_chi_sq",
                              partitions = 5,
                              lambda_vec = seq(0,300,by=20),
                              multiplier = 200,
                              c_seq_len = 50,
                              starts = big_starts)
```
```{r s1_m4_b_print, results = 'asis'}
s1_m4_b %>% report_results_2(., list_of_samples[[1]], report_eta = T)
```

@@

```{r s2_m4_b}
set.seed(2345)
s2_m4_b <- rre::cv_replicates(list_of_samples[[2]],
                              eval_function = "gof_chi_sq",
                              partitions = 5,
                              lambda_vec = seq(0,200,by=20),
                              multiplier = 200,
                              c_seq_len = 50,
                              starts = big_starts)
```
```{r s2_m4_b_print, results = 'asis'}
s2_m4_b%>% report_results_2(., list_of_samples[[2]], report_eta = T)
```

@@

### Sample 3
```{r s3_m4_a}
# big grids and few partitions to start:
set.seed(7654)
s3_m4_a <- rre::cv_replicates(list_of_samples[[3]],
                              eval_function = "gof_chi_sq",
                              partitions = 5,
                              lambda_vec = seq(0,1000,by=200),
                              multiplier = 200,
                              c_seq_len = 20)
```
```{r s3_m4_a_print, results = 'asis'}
s3_m4_a %>% report_results_2(., list_of_samples[[3]])
```

@@

```{r s3_m4_b}
# big grids and few partitions to start:
set.seed(7654)
s3_m4_b <- rre::cv_replicates(list_of_samples[[3]],
                              eval_function = "gof_chi_sq",
                              partitions = 5,
                              lambda_vec = seq(0,200,by=20),
                              multiplier = 200,
                              c_seq_len = 50,
                              starts = big_starts)
```
```{r s3_m4_b_print, results = 'asis'}
s3_m4_b %>% report_results_2(., list_of_samples[[3]], report_eta = T)
```
